SPARQL on the open, decentralised Web

### 2016-06-05 dissertation/introdefhistory.tex
Add a stub conclusions #9

This chapter serves to tie the accepted papers into a whole, provide
and overarching rationale and problem statements, overview of the
contributions and a discussion of the problematic sides of the study
seen from a philosophy of science viewpoint. It is structured as
follows: Section~\ref{sec:nodef} discusses the possibility of defining
the Semantic Web, Section~\ref{sec:objectivity} discusses the problem
of maintaining objectivity, Section~\ref{sec:history} attempts to
satisfy the previous discussion by detailing the author's personal
involvement in the Semantic Web. Section~\ref{sec:motivation} has an
overview of the motivation behind this work.
Section~\ref{sec:related} puts the present work into the context
within the existing literature. Section~\ref{sec:problems} summarises
important research problems and details the motivation, and
Section~\ref{sec:papersincontext} addresses how the contributions
address these problems and discusses weaknesses of the papers with the
benefit of hindsight.\todo{Big problem statement here}

>>>>

This chapter serves to tie the accepted papers into a whole, provide
and overarching rationale and problem statements, overview of the
contributions and a discussion of the problematic sides of the study
seen from a philosophy of science viewpoint. It is structured as
follows: Section~\ref{sec:nodef} discusses the possibility of defining
the Semantic Web, Section~\ref{sec:objectivity} discusses the problem
of maintaining objectivity, Section~\ref{sec:history} attempts to
satisfy the previous discussion by detailing the author's personal
involvement in the Semantic Web. Section~\ref{sec:motivation} has an
overview of the motivation behind this work.
Section~\ref{sec:related} puts the present work into the context
within the existing literature. Section~\ref{sec:problems} summarises
important research problems and details the motivation, and
Section~\ref{sec:papersincontext} addresses how the contributions
address these problems and discusses weaknesses of the papers with the
benefit of hindsight. Key insights are finally summarised in
Section~\ref{sec:conclusions}.\todo{Big problem statement here}
